---
title: "STA426 lesson materials: High-dimensional cytometry data analysis (11 Dec 2017)"
author: "Lukas M. Weber"
date: "12/10/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

See slides.

- What is high-dimensional cytometry?
- Automated data analysis
- Nowicka et al. (2017): CyTOF workflow for differential discovery in high-dimensional cytometry data sets
- Bioconductor



# Install Bioconductor

```{r}
source("https://bioconductor.org/biocLite.R")
biocLite()
```



# Download and install workflow package

The CyTOF data analysis workflow (Nowicka et al., 2017) is available for download as a "workflow package" from the Bioconductor website.

It can be installed as follows:

```{r}
source("https://bioconductor.org/workflows.R")
workflowInstall("cytofWorkflow")
```



# Data import

Notes:

- Description of BCR-XL data set: see Bioconductor workflow
- Explanation of .fcs files
- Preprocessing: normalization, de-barcoding, compensation, removal of dead cells and doublets


Check working directory:

```{r}
getwd()
```


Then continue by following the steps in the main workflow script "cytofWorkflow.R".



# Exercise

Perform a "null comparison" using code and data from the CyTOF workflow.

–  e.g. 4 vs. 4 comparison of "Reference" samples only
–  modify inputs to the differential testing / plotting functions and re-run the analysis
–  what do we expect? what do the results show?



